A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-08-01 papers/paper1/ms.tex
Rearrange and rewrite some text

\subsection{Starspot contrast and temperature}
There does not appear to be a first-principles theoretical prediction for the spectrum of a starspot, as a function of the physical state of the star.  Instead, practitioners have come up with phenomenological models based on observed trends in spot contrast coupled with ostensibly commonsense heuristics.  Most practitioners assume that starspot temperature depends principally on the photospheric temperature.  Two sources provide similar but slightly different trends for this relationship.  \citet{2019AJ....157...96R} distilled the compilation of spot temperatures from \citet{2005LRSP....2....8B} into a simple first order linear relationship:
\begin{equation}
  T_{\mathrm{spot}} = 0.418 \times T_{\mathrm{phot}} + 1620~\mathrm{K}
  \label{eq:Tspot}
\end{equation}

\citet{2016MNRAS.463.2494F} report an ostensibly quadratic dependence on the ambient photosphere, with hot stars asympoting to a typical starspot temperature of $\sim3500~\mathrm{K}$.  This departure from the linear trend could encode an observational bias since the LAMOST TiO-based technique may lack sensitivity to hypotetical hotter spots.  Nevertheless the trend serves as a useful guide in the absence of more, and higher quality, data.  Here we fit a quadratic relationship to the \citet{2016MNRAS.463.2494F} LAMOST-derived temperature points to obtain the relationship:
\authorcomment1{Ryan H. to determine A, B, and C}.

@@

@@

Starspots emit light, which is often parameterized as \emph{spot contrast}, $c$, where $0$ means the spots are completely black compared to the bright photosphere, and $c=0.3$ means the spot has 30\% the flux per-unit-surface-area of the pristine photosphere.  Hypothetically, a contrast of unity would mean the starspot blends into ambient photosphere, its border vanishing entirely.  Spot contrast is wavelength dependent ($c_\lambda$). It has a spectrum of its own, starting close to zero in the blue/visible, and approaching perhaps 40\% in the near-IR; the exact prescription remains an active research area \cite{2005LRSP....2....8B}.  Zeeman splitting and other magnetic phenomena are secondary to the mere fact that starspots appear as cooler-than-average regions on the stellar surface.

This equation is approximate, and in practice our team will derive $\mathcal{R}= \frac{c_{\tess}}{c_{\ktwo}}$ with Monte Carlo methods to take into account the uncertainty of the amplitude determination and subtle starspot self-dilution effects.
\newline

>>>>

\subsection{Starspot contrast}
Starspots emit light, which is often parameterized as spot contrast, $c$, where $0$ means the spots are completely black compared to the bright photosphere, and $c=0.3$ means the spot has 30\% the flux per-unit-surface-area of the pristine photosphere.  Hypothetically, a contrast of unity would mean the starspot blends into ambient photosphere, its border vanishing entirely.  Spot contrast is wavelength dependent ($c_\lambda$). It has a spectrum of its own, starting close to zero in the blue/visible, and approaching perhaps 40\% in the near-IR.

There does not appear to be a first-principles theoretical prediction for the spectrum of a starspot as a function of the fundamental properties of the star.  Instead, practitioners have come up with phenomenological models based on observed trends in spot contrast coupled with ostensibly commonsense heuristics.  For example, most practitioners assume that starspot temperature depends principally on the photospheric temperature.  Two sources provide similar but slightly different trends for this relationship.  \citet{2019AJ....157...96R} distilled the compilation of spot temperatures from \citet{2005LRSP....2....8B} into a simple first order linear relationship:
\begin{equation}
  T_{\mathrm{spot}} = 0.418 \times T_{\mathrm{phot}} + 1620~\mathrm{K}
  \label{eq:Tspot}
\end{equation}

\citet{2016MNRAS.463.2494F} report an ostensibly quadratic dependence on the ambient photosphere, with hot stars asympoting to a typical starspot temperature of $\sim3500~\mathrm{K}$.  This departure from the linear trend could be real, or may encode an observational bias since the LAMOST TiO-based technique may lack sensitivity to hypotetical hotter spots.  Nevertheless the trend serves as a useful guide in the absence of more, and higher quality, data.  Here we fit a quadratic relationship to the \citet{2016MNRAS.463.2494F} LAMOST-derived temperature points to obtain the relationship:
\authorcomment1{Ryan H. to determine A, B, and C}.

@@

This equation is approximate, and in practice our team will derive $\mathcal{R}= \frac{c_{\tess}}{c_{\ktwo}}$ with Monte Carlo methods to take into account the uncertainty of the amplitude determination and subtle starspot self-dilution effects.

@@
